---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# kakashi theme for xaringan

kakashi is a theme for the [xaringan R package](https://github.com/yihui/xaringan) for making slides. kakashi has a clean look with color-blind friendly palettes. 

Marking text as italics (&ast;) will turn it blue, bold (&ast;&ast;) will turn it orange, and striking out (~~) will turn it grey.

kakashi copies ideas from many other themes, including metropolis and lucy, but is ultimately unique. That is why this CSS (copy shinobi style) is called kakashi, [after the copy ninja](https://www.wikiwand.com/en/Kakashi_Hatake).

# Will you eventually contribute this theme to xaringan directly?

Yes, when I feel it is done. I've been using it for a while, but I still feel it needs polishing. In the mean time, you can include it in your slides using an R Markdown code chunk with the following code:

```{r, eval = FALSE}
htmltools::includeCSS("https://raw.githubusercontent.com/malcolmbarrett/kakashi/master/kakashi.css")
```

# Examples

+ [Advanced R Bookclub](https://advr-bookclub-24-25.netlify.com/)
+ [Functional programming and iteration with purrr](https://lar-purrr.netlify.com/)

